True versus apparent shapes of bow shocks

### 2018-03-07 papers/paper1-submit/latexdiff/ms-bows02-expand.tex
Final version with latexdiff to show changes

\makeatletter
%% Bundled custom packages
\newlength{\table@note@skip}
\setlength{\table@note@skip}{0.5ex}
\def\@eapj@cap@font{\bfseries}
\gdef\tblnote@list{}
\gdef\tblref@list{}
\newcommand\tablecomments[1]{\@tablecom{#1}}% 
\newcommand\tablerefs[1]{\@tableref{#1}}% 
\def\@tablecom#1{% 
 \vspace*{\table@note@skip}
\par 
{\parbox{\linewidth}{\hskip1em\rmfamily {\@eapj@cap@font Note}. --- #1}\par}% 
}% 
\def\@tableref#1{% 
 \vspace*{\table@note@skip}
\par 
{\parbox{\linewidth}{\hskip1em\rmfamily {\@eapj@cap@font References}. --- #1}\par}% 
}% 
\def\spew@tblnotes{% 
 \@ifx@empty\tblref@list{}{% 
  \@tablenotes{\tblref@list}%
  \vspace*{\table@note@skip}%
  \global\let\tblref@list\@empty 
 }% 
 \@ifx@empty\tblnote@list{}{% 
  \@tablenotes{\tblnote@list}% 
  \vspace*{\table@note@skip}%
  \global\let\tblnote@list\@empty
 }
 \the\DT@p@ftn%
}% 
\def\@tablenotes#1{% 
 \par 
% \footnoterule% 
 {\@table@type@size#1}% 
}%

\def\tabletypesize#1{\def\table@hook{#1}\gdef\@table@type@size{#1}}
\tabletypesize{\footnotesize}

\global\let\tablenotemark\relax
\global\def\tablenotemark#1{{\normalfont\textsuperscript{#1}}}
\global\let\tablenotetext\relax
% \global\def\tablenotetext#1#2{\footnotetext[#1]{\@table@type@size#2}} 
\global\def\tablenotetext#1#2{\noindent\textsuperscript{#1}{\@table@type@size#2}}

\newcommand\nodata{ ~$\cdots$~ }%

\newcommand\phn{\phantom{0}}% 
\newcommand\phd{\phantom{.}}% 
\newcommand\phs{\phantom{$-$}}% 
\newcommand\phm[1]{\phantom{#1}}% 
\makeatother

@@

We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grant Programa de Apoyo a Proyectos de Investigación e
Inovación Tecnológica IN111215.  JATY acknowledges support via a
research studentship from Consejo Nacional de Ciencias y Tecnología,
Mexico.  This work has made extensive use of Python language libraries
from the SciPy \citep{Jones:2001a} and AstroPy
\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a}
projects.  We appreciate the thoughtful comments of the anonymous
referee, which were led us to clarify the presentation of our results
and prompted the addition of \S~\ref{sec:obs}.

>>>>

%% Bundled custom packages
\usepackage{aastex-compat}

@@

We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grant Programa de Apoyo a Proyectos de Investigación e
Inovación Tecnológica IN111215.  JATY acknowledges support via a
research studentship from Consejo Nacional de Ciencias y Tecnología,
Mexico.  This work has made extensive use of Python language libraries
from the SciPy \citep{Jones:2001a} and AstroPy
\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a}
projects.  We appreciate the thoughtful comments of the anonymous
referee, which led us to clarify the presentation of our results and
prompted the addition of \S~\ref{sec:obs} and
Appendices~\ref{sec:radius-curvature}
and~\ref{sec:plane-sky-projection}.
